Modelling $q_{95}$ Windows for the Suppression of Edge Localized Modes by Resonant Magnetic Perturbations in the DIII-D Tokamak

### 2020-07-17 ExperimentalData/DIIID/145380/Paper/paper.tex
Modifications to paper

\begin{abstract}
A toroidal asymptotic matching model of the response of a tokamak plasma to a static resonant magnetic perturbation (RMP) is used to simulate the $n=3$ RMP-induced 
edge-localized-mode (ELM)-suppression
windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
derived from experimental measurements, apart from the neutral particle data. 
Three cases are considered.
In the first case, the natural frequencies of tearing modes resonant in the plasma are 
determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear theory.
In the second case, the natural frequencies are 
determined by the guiding center flows at the rational surfaces.
 In the third case, the natural frequencies   are 
determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives by far the worst agreement between the simulations 
and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
may be a consequence of using an inaccurate guess for the neutral particle distribution in the pedestal.  
\end{abstract}

@@

A second possibility is that a tearing mode is convected by the local guiding center fluid at the rational surface,\cite{heyn,paz1}
in which case we would expect the natural frequency to take the form 
\begin{equation}\label{e3}
\varpi_{\perp\, EB} =-n\,\omega_E.
\end{equation}
As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
at the rational magnetic flux-surface.

@@

Figure~\ref{fig4} shows the safety-factor in DIII-D discharge \#145380 as a function of time. It can be seen
that $q_{95}\equiv q({\mit\Psi}_N=0.95)$ varies from about 4.1 at the start of the current ramp to about 3.3
at the end. However, the safety-factor at the magnetic axis, $q_0 \equiv q({\mit\Psi}_N=0.0)$, remains approximately
constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. The centers of the
first, second, and third ELM-suppression windows correspond to $q_{95}\simeq 3.95$, 3.60, and 3.48, respectively.

@@

The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of time.
The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
expected flattening of the density and temperature profiles across the chains. Moreover, the driven island chains at the
bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
of Fig.~\ref{fig6} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width.

Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
island chains driven by the RMP in the pedestal region as functions of time. (See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity shown in Fig.~\ref{fig3}  is used to calculate the
critical island width for electron temperature flattening, whereas the corresponding particle diffusivity is used to calculate
the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
to significantly flatten the density and electron temperature profiles,  implying that there is actually very little degradation of the pedestal energy and particle confinement
due to the applied RMP. 
However, in those situations in which the shielding of driven
magnetic reconnection due to plasma flow breaks down (i.e., the true natural frequency becomes zero), locked magnetic island chains are generated that are
 wide enough to flatten both the density and the electron temperature profiles.

@@

\subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
The second case that we shall consider is that in which the natural frequency is determined by the local guiding center fluid; 
in other words, the natural frequency is specified by Eq.~(\ref{e3}).

@@

Three cases are considered. In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the guiding center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the electron flows at the corresponding rational surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}

@@

\section*{Acknowledgements}
This research was funded by the U.S.\ Department of Energy under contract DE-FG02-04ER-54742.
The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.

@@

@@

\subsection{Natural Frequency}\label{natural}
The natural frequency of a (stable) tearing mode is
the helical phase velocity with which it would propagate
were it actually unstable.\cite{rfa} The natural frequency
is determined by the equilibrium plasma flow at the
rational surface. Now, a magnetic island is a helical
pattern in the magnetic field  generated by a helical current perturbation that is localized in the
vicinity of the rational surface.
Given that plasma current is predominately carried by the
electrons, it is natural to suppose that a magnetic
island chain (as well as the tearing mode perturbation
away from the rational surface)  is convected by the
electron fluid in the immediate vicinity of the rational
surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
convected by the electron fluid at the rational surface then it propagates with respect to the local ion fluid. However, this is not a
problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
the ion fluid is not tied to the magnetic structure of the island chain. The situation is very different in the nonlinear regime. 
As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the rational
surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.

@@

\begin{figure}
\includegraphics[height=6in]{fig5.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig5}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig6.pdf}
\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  Full $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig7.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig8.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig8}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig9.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig10.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig11.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, 
purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig11}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig12.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig13.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}
\end{figure}

>>>>

\begin{abstract}
A toroidal asymptotic matching model of the response of a tokamak plasma to a static resonant magnetic perturbation (RMP) is used to simulate the $n=3$ RMP-induced 
edge-localized-mode (ELM)-suppression
windows in $q_{95}$ that are evident when the plasma current is slowly ramped in DIII-D discharge \#145380. All quantities employed in the simulation are
derived from experimental measurements, apart from the neutral particle data. 
Three cases are considered.
In the first case, the natural frequencies of tearing modes resonant in the plasma are 
determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear theory.
In the second case, the natural frequencies are 
determined by the guiding-center flows at the rational surfaces.
 In the third case, the natural frequencies   are 
determined by the electron flows at the  rational surfaces, which is the prediction of linear theory.
The second case gives  the best agreement between the simulations and the  experimental observations.   The third case gives by far the worst agreement between the simulations 
and the  observations. The first case only leads to partial agreement between  the  simulations and the  observations. However, this lack of complete agreement
may be a consequence of using an inaccurate guess for the neutral particle distribution in the pedestal.  
\end{abstract}

@@

A second possibility is that a tearing mode is convected by the local guiding-center fluid at the rational surface  (again, see the discussion in Sect.~\ref{natural}),\cite{heyn,paz1}
in which case we would expect the natural frequency to take the form 
\begin{equation}\label{e3}
\varpi_{\perp\, EB} =-n\,\omega_E.
\end{equation}
As before, the right-hand side of Eq.~(\ref{e3}) is evaluated
at the rational magnetic flux-surface.

@@

Figure~\ref{fig4} shows the safety-factor in DIII-D discharge \#145380 as a function of time. It can be seen
that $q_{95}\equiv q({\mit\Psi}_N=0.95)$ varies from about 4.1 at the start of the current ramp to about 3.3
at the end. However, the safety-factor at the magnetic axis, $q_0 \equiv q({\mit\Psi}_N=0.0)$, remains approximately
constant at about 1.0. For the sake of practicality,  the {\tt GPEC} and {\tt EPEC} calculations described in this paper ignore $n=3$ rational
surfaces that lie very close to the LCFS: in other words,  surfaces that lie in the region $0.997 < {\mit\Psi}_N\leq 1.000$. Let $\overline{q_{95}}\equiv 5.2060-0.4457\,t$ represent the
least-squares linear fit to the $q_{95}$ versus time data shown in Fig.~\ref{fig4}. 
It follows that the 
first, second, and third ELM-suppression windows extend over the $\overline{q_{95}}$ ranges $3.88$--$3.94$, $3.62$--$3.73$,
and $3.33$--$3.48$, respectively.

@@

The upper panel of Fig.~\ref{fig6} shows the widths of the various vacuum magnetic island chains driven by the applied $n=3$ RMP in the pedestal region as functions of $
\overline{q_{95}}$.
The vacuum island widths are the  expected island widths in the absence of any shielding of driven magnetic reconnection due to
plasma flow; in other words, they are the  widths of the island chains that would be driven if all of the natural frequencies were zero. It can be seen that
the driven magnetic island chains extend over most of the pedestal, implying a very significant degradation in pedestal energy and particle confinement due to the
expected flattening of the density and temperature profiles across the chains. Moreover, the driven island chains at the
bottom of the pedestal overlap, implying that the magnetic field in this region is rendered stochastic. The lower panel
of Fig.~\ref{fig6} shows the actual widths of the various magnetic island chains driven by the applied $n=3$ RMP as functions of time. It is apparent 
that the true island widths are generally much smaller than the vacuum island widths, as a consequence of the shielding of driven magnetic
reconnection due to plasma flow. However, the shielding breaks down at various rational surfaces when the associated natural frequency is zero (see the lower panel of
Fig.~\ref{fig5}). In this situation, the driven island width is similar to the vacuum island width. Note that Fig.~\ref{fig6} is similar in conception to
Fig.~23 of Ref.~\onlinecite{wade}.

Figure~\ref{fig7} shows the widths of the regions of density and electron temperature flattening associated with the $n=3$ magnetic
island chains driven by the RMP in the pedestal region as functions of $\overline{q_{95}}$ and time. (See Sect.~III.F in Ref.~\onlinecite{rf2}.) (Note that the energy diffusivity data shown in Fig.~\ref{fig3}  is used to calculate the
critical island width for electron temperature flattening, whereas the corresponding particle diffusivity data is used to calculate
the critical island width for density flattening.\cite{flat}) It can be seen that the driven magnetic island chains are generally too narrow
to significantly flatten the density and electron temperature profiles,  implying that there is actually very little degradation of the pedestal energy and particle confinement
due to the applied RMP. 
However, in those situations in which the shielding of driven
magnetic reconnection due to plasma flow breaks down (i.e., the true natural frequency becomes zero), locked magnetic island chains are generated that are
 wide enough to flatten both the density and the electron temperature profiles.

@@

\subsection{Case 2: $\varpi=\varpi_{\perp\,EB}$}
The second case that we shall consider is that in which the natural frequency is determined by the local guiding-center fluid; 
in other words, the natural frequency is specified by Eq.~(\ref{e3}).

@@

Three cases are considered. In the first case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the ion flows at the corresponding rational surfaces, which is the prediction of nonlinear tearing mode theory.\cite{nl1,nl2,nl3}
In the second case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the guiding-center flows at the corresponding rational surfaces.\cite{heyn,paz1} 
In the third case, the natural frequencies of (stable) $n=3$ tearing modes, resonant in the plasma, are assumed to be
determined by the electron flows at the corresponding rational surfaces, which is the prediction of linear tearing mode theory.\cite{lin1,lin2,lin3}

@@

\section*{Acknowledgements}
The author would like to thank Q.M.~Hu and R.~Nazikian for providing the experimental data used in this paper. The
author would also like to thank J.-K.~Park and N.C.~Logan for providing guidance on how to run the {\tt GPEC} code.
This research was directly funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences,  under contract DE-FG02-04ER54742, and
incorporates work funded by the U.S.\ Department of Energy, Office of Science, Office of Fusion Energy Sciences, using the DIII-D National Fusion Facility, a DOE Office of Science user facility, under contract DE-FC02-04ER54698.

\section*{Disclaimer} This report was prepared as an account of work sponsored by an agency of the United States Government. Neither the United States Government nor any agency thereof, nor any of their employees, makes any warranty, express or implied, or assumes any legal liability or responsibility for the accuracy, completeness, or usefulness of any information, apparatus, product, or process disclosed, or represents that its use would not infringe privately owned rights. Reference herein to any specific commercial product, process, or service by trade name, trademark, manufacturer, or otherwise does not necessarily constitute or imply its endorsement, recommendation, or favoring by the United States Government or any agency thereof. The views and opinions of authors expressed herein do not necessarily state or reflect those of the United States Government or any agency thereof.

@@

\bibitem{wade} M.R.~Wade, R.~Nazikian, J.D.~de\,Grassie, T.E.~Evans, N.M.~Ferraro, R.A.~Moyer, D.M.~Orlov, 
R.J.~Buttery, M.E.~Fenstermacher, A.M.~Garofalo, {\em et al.}, Nucl.\ Fusion {\bf 55}, 023002 (2015).

@@

\subsection{Natural Frequency}\label{natural}
The natural frequency of a (stable) tearing mode is
the helical phase velocity with which it would propagate
were it actually unstable.\cite{rfa} The natural frequency
is determined by the equilibrium plasma flow at the
rational surface. Now, a magnetic island is a helical
pattern in the magnetic field  generated by a helical current perturbation that is localized in the
vicinity of the rational surface.
Given that plasma current is predominately carried by the
electrons, it is natural to suppose that a magnetic
island chain (as well as the tearing mode perturbation
away from the rational surface)  is convected by the
electron fluid in the immediate vicinity of the rational
surface. This is indeed the case in the linear regime.\cite{ara} Of course, as a consequence of diamagnetic flows, if the island chain is
convected by the electron fluid at the rational surface then it propagates with respect to the local ion fluid. However, this is not a
problem because a linear layer is sufficiently thin that the magnetic field can diffuse through the plasma very rapidly, which implies that
the ion fluid is not tied to the magnetic structure of the island chain.

The situation is very different in the nonlinear regime. 
As we have seen, the region inside the magnetic separatrix of a nonlinear magnetic island chain is governed by a combination of flux-freezing and perturbed force balance.
This implies that both the electron and the ion fluids are trapped inside the separatrix, and are, therefore,  forced to co-rotate with the island chain. There
is no such constraint outside the separatrix, so the electron and ion fluids rotate at different speeds in this region,
as a consequence of diamagnetism.  It follows that one or other of the electron and the ion fluid rotation profiles must exhibit a strong gradient across
the separatrix. The island propagation velocity is determined by which of the two fluids is most resistant to the formation of such a gradient. 
Of course, it is the ion fluid which is more resistant because of its much greater perpendicular viscosity,\cite{nl1,wat} as well as its much larger 
neoclassical stress tensor.\cite{nl2} Hence, a nonlinear magnetic island chain is convected by the ion fluid in the vicinity of the rational
surface, because this choice of propagation speed minimizes the ion fluid velocity gradient across the separatrix.

Finally, we could imagine that if the width of an island chain is neither much less than the linear layer width (which is the strict
criterion for the validity of linear theory) nor much greater than the linear layer width (which is the strict criterion for
the validity of nonlinear theory) then the chain lies in some sort of intermediate regime in which it is
convected by the local guiding-center fluid (which is intermediate between the predictions of linear and nonlinear theory).

@@

\begin{figure}
\includegraphics[height=6in]{fig5.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig5}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig6.pdf}
\caption{Top Panel: Full  $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time 
in   DIII-D discharge \#145380.
Bottom Panel:  Full $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig6}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig7.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by nonlinear island physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig7}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig8.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency. The red, green, blue, yellow, cyan, magenta, brown, pink,
purple, and orange  curves correspond to $m=5$, 6, 7, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig8}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig9.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig9}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig10.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is  determined by the ${\bf E}\times {\bf B}$
frequency.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by the ${\bf E}\times {\bf B}$
frequency. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig10}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig11.pdf}
\caption{Top Panel: $n=3$ natural frequencies, in absence of RMP, as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  $n=3$ natural frequencies, in presence of RMP, as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The black, red, green, blue, yellow, cyan, magenta,  brown, 
purple, and orange curves correspond to $m=4$, 5, 6, 7, 8, 9, 10,  11, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows.} \label{fig11}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig12.pdf}
\caption{Top Panel: $n=3$ vacuum island widths as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380.
Bottom Panel:  $n=3$ island widths as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig12}
\end{figure}

\begin{figure}
\includegraphics[height=6in]{fig13.pdf}
\caption{Top Panel: Density flattening widths associated with induced $n=3$ magnetic island  chains as functions of the least-squares linear fit to $q_{95}$ versus time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics.
Bottom Panel:  Electron temperature flattening widths associated with induced $n=3$ magnetic island chains as functions of time
in   DIII-D discharge \#145380, assuming that the natural frequency is determined by linear layer physics. The blue, yellow, cyan, magenta, brown, pink,
purple, and orange  areas correspond to $m=7$, 8, 9, 10, 11, 12, 13, and 14, respectively. The yellow vertical bands indicate the ELM-suppression windows. 
The horizontal dotted lines indicate  the top of the pedestal, ${\mit\Psi}_N=0.925$.} \label{fig13}
\end{figure}
